Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-23 Paper.tex
Update Paper.tex

Le commissioni per lo storage hanno have a slightly nuanced behaviour---to incentivise minimisation of the use of storage (which corresponds directly to a larger state database on all nodes), the execution fee for an operation that clears an entry in the storage is not only waived, a qualified refund is given; in fact, this refund is effectively paid up-front since the initial usage of a storage location costs substantially more than normal usage.

>>>>

Le commissioni per lo storage hanno un comportamento leggermente sfumato---per incentivare il decremento dell'uso dello storage (
che corrisponde direttamente a un database di stato maggiore su tutti i nodi), la commissione di esecuzione per un'operazione che cancella una voce nello storage non è solo waived, a qualified refund is given; in fact, this refund is effectively paid up-front since the initial usage of a storage location costs substantially more than normal usage.
